### 2017-05-13 paper/evaluation.tex
pass on RQ7

To answer this research question, we ran ten different subjects
against all configurations described in Section~\ref{sec:modes} and
compared their running times and rate of test flakiness.  We selected
subjects from the medium and long groups listed in
Section~\ref{sec:rqA} and ran their longest test module for testing.
The rationale is to obtain a diverse set of subjects exposing a wide
range of running times (range observed 1.1m-8.2m) and number of test
cases (range observed 54-17,513).  The rationale for fixing the number
of subjects in ten was to be able to finish execution in reasonable
time.  We ran each project on each configuration with ten seeds and
reported averages of time and flakiness.  Overall, we need to reran
test suites 600 times, 60 times (10x6 configurations) on each project.

@@

To compare flakiness and efficiency, we used the sequential execution
of each subject's test suite as the \emph{control group} (\ie,
baseline). Notice that with parallelism enabled, the number of failing
tests may vary on different runs due to the non-deterministic
scheduling of threads and processes.  For that reason, we re-executed
the experiment and computed the average speedup and flakiness on each
scenario.

@@

>>>>

To answer this research question, we ran ten different subjects
against all configurations described in Section~\ref{sec:modes} and
compared their running times and rate of test flakiness.  We used the
sequential execution (configuration \emph{\Seq{}}) associated with
each project as the comparison baseline in this experiment.  We
selected subjects from the medium and long groups from
Section~\ref{sec:rqA} and further selected their longest test module
for testing.  The rationale is to obtain a diverse set of subjects
exposing a wide range of running times (range observed 1.1m-8.2m) and
number of test cases (range observed 54-17,513) and yet be able to run
the experiment in reasonable time.  We ran each project on each
configuration with ten seeds.  Overall, we needed to reran test suites
600 times, 60 times (10x6 configurations) on each project.  Given the
low standard deviations observed in our measurements we consider ten
seeds reasonable for this experiment.

@@

%% Notice that with parallelism enabled, the
%% number of failing tests may vary on different runs due to the
%% non-deterministic scheduling of threads and processes.  For that
%% reason, we re-executed the experiment and computed the average speedup
%% and flakiness on each scenario.

@@

\Mar{...estou aqui...}
